---
title: "Improved ISCAM"
author: "DongWon Jung"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, label = "SETUP", echo = FALSE, results= 'hide', message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(comment = NA, fig.align = 'center', fig.height = 5, fig.width = 5, prompt = FALSE, 
highlight = TRUE, tidy = FALSE, warning = FALSE, message = FALSE, 
tidy.opts=list(blank = TRUE, width.cutoff = 80))
```

## Introduction. 

Our statistic class use Investigating Statistical Concepts, Applications, and Methods (ISCAM) by Beth L.Chance and Allan J.Rossman. The way [ISCAM](http://www.rossmanchance.com/iscam3/files.html) also involve with `R` code but this is not a easy way to use. Therefore, the goal is how to improve ISCAM. If you have ISCAM book, turn to page number 129. The book suggest use their `R` command to solve the problems. 

## Description 

These functions are provide a graphical representation for visual people to see which area we are compute. Order to use this package, it require install improved ISCAM.

`devtools::install_github("jungd/ImproveISCAM", build_vignette = TRUE)`

### Binomial Probability
Binomial probability refers to the probability that a binomial experiment results in exactly x successes.       
For example :
 
```{r}
library(ImproveISCAM)
binomprob(3,20,1/3,lower.tail = FALSE)
binomprob(3,20,1/3,lower.tail = TRUE)
```
As you see from my example, `binomial(k,n,pi,TRUE/FALSE)`. `lower.tail = FALSE` indicate right tail probability of binomial random variable. `lower.tail= TRUE` indicate left tail probability of binomial random variable. 

### Exact Binomial Test and Confidence Interval.
```{r}
binomtest(3, 13, 1/2, "greater")
```
`binomtest(k,n,pi,"greeter/less/tow.sided")` will help you determined right/left tail probability of binomial random variable. As you see the result, it already show null hypothesis and alternative hypothesis with p-value. So you can conclude with your result either reject null hypothesis or not. 

For example :

```{r, fig.width= 7, fig.height= 7}
binomtest(3, 13, conf.level=c(90,95))

```
`binomtest(k, conf.level = c( , ))` will calculate confidence interval for you. 

### Normal Probability
The normal distribution is a probability distribution that associates the normal random variable X with a cumulative probability.      

For example :   
```{r}
normprob(2, direction="above")
```
`normporb(x, mu, sigma, "above/below/outside/between")` will help calculate right.left/two-tailed probability and probability between tow values in normal distribution. 

### Inverse Normal Probability

```{r}
InNorm(0.88, direction="above")
InNorm(0.88, direction="between")
```
`InNorm(probability, direction="above/below/outside/between")` will calculate your z-score value with right/left/two-tail probability and probability between tow values.

### Normal(z-test) Approimation for One Propotion and Confidence Interval(CI)

```{r, fig.width= 5, fig.height=7}
propztest(2.67, 18, 1/3, "greater")

```
`propztest(k,n,pi, "greater/below/less/two.sided/")` will find right/left/two-tailed probabilty of proportion using Normal z-test. 

```{r, fig.width=7, fig.height=7, }
propztest(3, 13, conf.level=c(90,95))
```
`propztest(k,n,conf.level=c( ,))` will hlep you find normal confidce interval. 



